Rationality, Evolution \& the Environment

### 2015-08-21 paper/paper.tex
edits result section

\title{Rationality, Evolution \& the Environment}
\author{Paolo Galeazzi \& Michael Franke}
\date{current version: May 27th 2015}

\begin{document}
\maketitle

@@

EXAMPLE 1: \textit{Coordination Game.}

Let us consider the coordination game in Figure \ref{coordgame1}.

@@

It is easy to see that $\text{reg}(I)=2$: when the other player chooses action $I$ the regret of $I$ is $0$ since $I$ is a best reply to $I$, and when the other player chooses $II$ the regret of $I$ is $2$ since $\pi_i(II,II)-\pi_i(I,II)=2$. With the same reasoning, $\text{reg}(II)=1$. Two regret minimizing players would then choose action $II$, each getting a payoff of $2$. In this case regret minimization selects the Pareto-dominant Nash equilibrium. $ \medsquare $

\vspace{.5cm}

EXAMPLE 2: \textit{The Traveller's Dilemma.} (HalpernPass12)

Let us now consider the Traveller's Dilemma case. The story behind the game goes as follows. There are two travellers, Ann and Bob, who lost their luggages. Ann and Bob had exactly the same luggage and they had insured the luggages with the same insurance company. The insurance policy is that the two travellers have to separately claim a certain amount between 2\$ and 100\$ for the reimbursement, and if they both claim the same amount then they will be reimbursed by that amount. Otherwise, if one of them claims more than the other, then the one who claimed the higher amount will get the lower amount minus 2\$, while the one who claimed the lower amount will get what (s)he claimed plus 2\$. The game is symmetric, and the payoff function for both players is:\\
$\pi_i(a_i,a_{-i}) =  \begin{cases} a_i \text{ \hspace{1cm} if } a_i = a_{-i} \\ a_i + 2 \text{ \hspace{.4cm} if } a_i < a_{-i} \\ a_{-i} -2 \text{ \hspace{.25cm} if } a_{-i} < a_i \end{cases}$ \\
By a simple computation we have:  $\forall a_i \in \lbrace 96\$, ..., 100\$ \rbrace \text{, } \text{reg}(a_i)=3 $ and $\forall a_i \in \lbrace 2\$, ..., 95\$ \rbrace \text{, } \text{reg}(a_i)>3$. If we now eliminate all the actions that do not minimize regret in the first place and iterate the regret minimization only on the action set $\lbrace 96\$, ..., 100\$ \rbrace$, we get that 97\$ is the action that minimize regret. Indeed, $\text{reg}(97)=2$ and $\forall a_i \in \lbrace 96\$, 98\$, 99\$, 100\$ \rbrace \text{, } \text{reg}(a_i)=3 $. Hence, one step of regret minimizing reasoning eliminates all the actions smaller than 96\$, and if we iterate the process once more the unique outcome is 97\$. Finally, it is worth noticing that the only rationalizable equilibrium of the game corresponds to the outcome $(2,2)$, that is consequently the only Nash equilibrium, the only perfect equilibrium, and the only sequential equilibrium of the game. $ \medsquare $\\

@@

Table~\ref{tab:ExpectedFitness_4Types} gives an approximation of expected fitness, obtained
from averaging over randomly sampled $100,000$ games in $\mathcal{G}$ with
$a,b,c,d \in \lbrace 0, \dots, 10 \rbrace$. The number in each cell corresponds to the average
evolutionary fitness of the row player when matched with the column player. Whenever a player
type would not select a unique action in a given game, we recorded unbiased averages over
playing either.

@@

Simulation results reflect Fact~\ref{fact:equivalence2x2} in that all encounters in which
types $\tau^{reg}, \Delta(A_{-i})$, $\tau^{reg}, \overline{\mu}$ or $\tau^{\pi},
\overline{\mu}$ are substituted for one another yield identical results. More interestingly,
Table~\ref{tab:ExpectedFitness_4Types} shows that the maximin strategy $\tau^{\pi},
\Delta(A_{-i})$ is strictly dominated by either of the three other strategies: in each row
column (i.e., for each kind of opponent), the maximin strategy is strictly worse than any of
the three behaviorally equivalent competitors. This has a number of interesting consequences.

Firstly, if we restrict attention to a population of radically uncertain players where only
epistemic type exists $\Delta(A_{-i})$, the regret type $ \tau^{reg} $ is the only
evolutionarily stable state; we expect selection that is driven by expected fitness to
invariably weed out maximin behavior in favor of regret minimization. In other words, in the
class of random games looked at here, regret minimization is a better choice rule than standard
maxmin from an evolutionary point of view.

Secondly, if we look at the competition between all four types represented in
Table~\ref{tab:ExpectedFitness_4Types}, $\tau^{reg}, \Delta(A_{-i})$ is no longer the only
evolutionarily stable type in this meta-game. Rather, given behavioral equivalence
(Fact~\ref{fact:equivalence2x2}), types $(\tau^{reg}, \Delta(A_{-i}))$,
$(\tau^{reg}, \overline{\mu})$, and $(\tau^{\pi}, \overline{\mu})$ are all neutrally stable
\citep{Maynard-Smith1982:Evolution-and-t}, while $(\tau^{\pi}, \Delta(A_{-i}))$ is strictly
dominated and so disfavored by fitness-based selection. Based on considerations of evolutionary
stability in this meta-game, we are drawn to conclude that maximin behavior is weeded out in
favor of a population with a random distribution of the remaining three types.

Simulation results of the (discrete time) \emph{replicator dynamics}
\citep{TaylorJonker1978:Evolutionary-St} indeed show that random initial population
configurations are attracted to states with only three player types:
$\tuple{\tau^{reg}, \Delta(A)}$, $\tuple{\tau^{reg}, \bar{\mu}}$ and
$\tuple{\tau^{\pi}, \bar{\mu}}$. The relative proportions of these depend on the initial
population.

Interestingly, however, this variability is eradicated if we add a small mutation rate to the
dynamics. We assume a fixed, small mutation rate $\epsilon$ for the probability that a player's
preference type \emph{or} her epistemic type changes to another random preference type or
epistemic type. The probability that a player type randomly mutates into a completely different
player type with altogether different preference type and epistemic type would then be
$\epsilon^2$. With these assumptions about ``local mutations'', numerical simulations of the
(discrete time) \emph{replicator mutator dynamics} \citep{Nowak2006:Evolutionary-Dy} show that
for very small mutation rates almost all initial populations converge to a single fixed point
in which the majority of players are regret types. For instance, with $\epsilon = 0.001$,
almost all initial populations are attracted to a final distribution with proportions:

@@

What this suggests is that, since biological evolution selects behavior-generating mechanisms,
not behavior as such, it need not be the case that behaviorally equivalent mechanisms are
treated equally all the while. If mutation probabilities are a function of individual
components of such behavior-generating mechanisms, it can be the case that certain components
are more strongly favored by a process of random mutation and selection. This is exactly the
case with regret-based subjective preferences in our little toy example here. Since
regret-based subjective preferences are much better in connection with radical uncertainty than
veridical preferences are, we see a majority of regret-based preference types paired with
probabilistic epistemic types. In sum, component-wise mutation could have lead to a majority of
regret-based players even if they are behaviorally indiscernible from decision makers with
veridical preferences.

@@

Results based on the single meta-game in Table~\ref{tab:Utils-MetaGame}, which was obtained by
averaging over numerical simulations, are not fully general and possibly spoiled by random
fluctuations in the sampling procedure. Fortunately, for the case of symmetric $2 \times 2$
games, the main result that maximin types $(\tau^{\pi}, \Delta(A_{-i}))$ are strictly dominated
can also be shown analytically for generous general conditions on the nature of $P(G)$.

@@

  Let $\Lambda = \lbrace (\tau^{\pi}, \Delta(A_{-i})), (\tau^{reg}, \Delta(A_{-i})) \rbrace$ be
  the set of possible players $(\tau, e)$ in the population, and let $\mathcal{G}$ be the class
  of symmetric $2 \times 2$ games with payoffs sampled from a finite, or compact and convex,
  set of i.i.d.~values. Then, $(\tau^{reg}, \Delta(A_{-i}))$ is the only strict Nash
  equilibrium in the resulting meta-game.

@@

Corollary~\ref{corollary1} tells us that the results obtained for the meta-game in
Table~\ref{tab:Utils-MetaGame} hold more generally for any class of games in which the
probability of encountering a game is the product of independently sampling four identically
distributed payoff values. As before, player types $(\tau^{reg}, \Delta(A_{-i}))$,
$(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg}, \overline{\mu})$ will be neutrally stable,
and fitness-based selection will tend to weed out maximin-players and leave us with a
population of arbitrary frequency of $(\tau^{reg}, \Delta(A_{-i}))$,
$(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg}, \overline{\mu})$ players.

@@

The basic results from the previous section demonstrate the main conceptual point that we
wanted to make: non-veridical subjective preference relations can persist under evolutionary
selection along a gradient of objective fitness. In particular, regret-based preferences can
not only persist, but even be favored by natural selection if agents are radically
uncertain. This holds generally for playing arbitrary $2 \times 2$ games whose payoffs are
sampled identically and independently at random.

How do the basic results from the previous section carry over to more encompassing, richer
models? Section~\ref{sec:more-types} first considers a further conceptually interesting
preference types that have been suggested in the recent literature. Section~XZY then looks at
the basic cast of player types, but considers the case of $n \times n$ games. Finally, to put
our results into the proper perspective, Section~XZY ends with a brief comparison of game
situations with cases of solitary decision making.

@@

The approximations in Table~\ref{tab:ExpectedFitness_2x2_Full} confirm basic
intuitions. Averaging over randomly sampled games, everybody would like to have an altruistic
opponent and nobody would like to play against a competitive opponent. Moreover, altruistic
types come up strictly dominated by competitive types, but competitive types themselves are
always worse than any of the behaviorally equivalent types $(\tau^{reg}, \Delta(A_{-i}))$,
$(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg}, \overline{\mu})$, except against maximin
players $\tuple{\tau^{\pi}, \Delta(A)}$. This is a noteworthy results in the light of the fact
that evolving altruistic preferences have been shown to support cooperative behavior in a
single stage game \myalert{[CITE]}.\todo{@Paolo: check whether this is true, please!} In
contrast, averaging over payoffs in multiple stage games, like we do here, makes altruistic
preferences prime victims of evolutionary eradication.

It is easy to see then that the previous result still obtains for the larger meta-game in
Table~\ref{tab:ExpectedFitness_2x2_Full}: $(\tau^{reg}, \Delta(A_{-i}))$,
$(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg}, \overline{\mu})$ are still neutrally stable;
all simulations of the (discrete-time) replicator dynamic end in populations consisting of only
these types in arbitrary proportion.

The following proposition confirms this result.\todo{rephrase to acknowledge all epistemic types}

@@

Results from Section~\ref{sec:results:-basic-model} relied heavily on
Fact~\ref{fact:equivalence2x2} that regret minimization $\tuple{\tau^{reg}, \Delta(A)}$ is
behaviorally equivalent with expected regret minimization $\tuple{\tau^{reg}, \bar{\mu}}$ and
expected utility maximization $\tuple{\tau^{\pi}, \bar{\mu}}$. This is no longer true when we
look at arbitrary $n \times n$ games with $n \ge 2$.

Table~\ref{tab:ExpectedFitness_10x10} therefore gives approximations for expected fitness in a
meta-game over a class over a class of $n \times n$ symmetric games where $n$ is randomly drawn
from $\set{2, \dots, 10}$. Concretely, the numbers in Table~\ref{tab:ExpectedFitness_10x10} are
averages of payoffs obtained in 100,000 randomly sampled games, where each game was sampled by
first picking a number of acts $n \in \set{2, \dots, 10}$ uniformly at random, and then filling
the resulting $n \times n$ payoff matrix of the stage game with i.i.d.~sampled payoffs as
before.

>>>>

\title{Rationality, Evolution \& the Environment}
\author{Paolo Galeazzi \& Michael Franke}
\date{current version: August 21st 2015}

\begin{document}

\textbf{some notes and remarks and todo's}

\begin{itemize}
\item micha: let's have a term for pairs (regret type, epistemic type); I'm inclined to use ``player
  type'', but that's what you reserved for regret type; maybe use \myalert{meta-type}?
\item 
\end{itemize}

\maketitle

@@

\begin{example}[Coordination Game]
  Let us consider the coordination game in Figure \ref{coordgame1}. It is easy to see that
  $\text{reg}(I)=2$: when the other player chooses action $I$ the regret of $I$ is $0$ since
  $I$ is a best reply to $I$, and when the other player chooses $II$ the regret of $I$ is $2$
  since $\pi_i(II,II)-\pi_i(I,II)=2$. With the same reasoning, $\text{reg}(II)=1$. Two regret
  minimizing players would then choose action $II$, each getting a payoff of $2$. In this case
  regret minimization selects the Pareto-dominant Nash equilibrium. $ \medsquare $

@@

\begin{example}[The Traveller's Dilemma \citep{HalpernPass2012:Iterated-Regret}]
Let us now consider the Traveller's Dilemma case. The story behind the game goes as
follows. There are two travellers, Ann and Bob, who lost their luggages. Ann and Bob had
exactly the same luggage and they had insured the luggages with the same insurance company. The
insurance policy is that the two travellers have to separately claim a certain amount between
2\$ and 100\$ for the reimbursement, and if they both claim the same amount then they will be
reimbursed by that amount. Otherwise, if one of them claims more than the other, then the one
who claimed the higher amount will get the lower amount minus 2\$, while the one who claimed
the lower amount will get what (s)he claimed plus 2\$. The game is symmetric, and the payoff
function for both players is:
\begin{align*}
  \pi_i(a_i,a_{-i}) = \begin{cases} a_i \text{ \hspace{1cm} if } a_i = a_{-i} \\ a_i + 2 \text{
      \hspace{.4cm} if } a_i < a_{-i} \\ a_{-i} -2 \text{ \hspace{.25cm} if } a_{-i} <
    a_i \end{cases}
\end{align*}
By a simple computation we have:  $\forall a_i \in \lbrace 96\$, ..., 100\$ \rbrace \text{, } \text{reg}(a_i)=3 $ and $\forall a_i \in \lbrace 2\$, ..., 95\$ \rbrace \text{, } \text{reg}(a_i)>3$. If we now eliminate all the actions that do not minimize regret in the first place and iterate the regret minimization only on the action set $\lbrace 96\$, ..., 100\$ \rbrace$, we get that 97\$ is the action that minimize regret. Indeed, $\text{reg}(97)=2$ and $\forall a_i \in \lbrace 96\$, 98\$, 99\$, 100\$ \rbrace \text{, } \text{reg}(a_i)=3 $. Hence, one step of regret minimizing reasoning eliminates all the actions smaller than 96\$, and if we iterate the process once more the unique outcome is 97\$. Finally, it is worth noticing that the only rationalizable equilibrium of the game corresponds to the outcome $(2,2)$, that is consequently the only Nash equilibrium, the only perfect equilibrium, and the only sequential equilibrium of the game. $ \medsquare $

@@

Table~\ref{tab:ExpectedFitness_4Types} gives an approximation of expected fitness, obtained by
numerical simulation from averaging over $100,000$ randomly sampled games in $\mathcal{G}$ with
$a,b,c,d \in \lbrace 0, \dots, 10 \rbrace$. Concretely, games were sampled repeatedly by
choosing independently four integers $a,b,c,d \in \lbrace 0, \dots, 10 \rbrace$ uniformly at
random. For each game, a player type's action choices were determined and payoffs from all
pairwise encounters recorded. (Whenever a player type would not select a unique action in a
given game, we recorded unbiased averages over playing either action.) The number in each cell
of Table~\ref{tab:ExpectedFitness_4Types} is the average payoff for the row player type over
all 100,000 numbers for each pairing of player types obtained in this way. These averages
approximate the corresponding average evolutionary fitness of the row player when matched with
the column player.

@@

Simulation results obviously reflect Fact~\ref{fact:equivalence2x2} in that all encounters in
which types $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{reg}, \overline{\mu})$ or
$(\tau^{\pi}, \overline{\mu})$ are substituted for one another yield identical results. More
interestingly, Table~\ref{tab:ExpectedFitness_4Types} shows that the maximin strategy
$(\tau^{\pi}, \Delta(A_{-i}))$ is strictly dominated by either of the three other strategies:
in each column (i.e., for each kind of opponent), the maximin strategy is strictly worse
than any of the three behaviorally equivalent competitors. This has a number of interesting
consequences.

Let's begin with a restricted scenario and look at more and more complex cases afterwards. If
we restrict attention to a population of radically uncertain players, i.e., where only
epistemic type $\Delta(A_{-i})$ exists, the regret type $ \tau^{reg} $ is the only
\emph{evolutionarily stable state}. An evolutionarily stable state is a state which cannot be
invaded by a small number of mutants. More strongly, since maximin play is strictly dominated,
we expect selection that is driven by expected fitness to invariably weed out maximin behavior
in favor of regret minimization. In other words, when taking average payoffs over the class of
random games looked at here, regret minimization is a better choice rule than standard maxmin
from an evolutionary point of view, despite the fact that the former, but not the letter
entertains non-veridical subjective preferences.

Next, if we look at the competition between all four types represented in
Table~\ref{tab:ExpectedFitness_4Types}, $(\tau^{reg}, \Delta(A_{-i}))$ is no longer
evolutionarily stable. Rather, given behavioral equivalence (Fact~\ref{fact:equivalence2x2}),
types $(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{reg}, \overline{\mu})$, and
$(\tau^{\pi}, \overline{\mu})$ are all \emph{neutrally stable}
\citep{Maynard-Smith1982:Evolution-and-t}. But since $(\tau^{\pi}, \Delta(A_{-i}))$ is strictly
dominated and so disfavored by fitness-based selection, we are still drawn to conclude that
maximin behavior is weeded out in favor of a population with a random distribution of the
remaining three types.

Simulation results of the (discrete time) \emph{replicator dynamics}
\citep{TaylorJonker1978:Evolutionary-St} indeed show that random initial population
configurations are attracted to states with only three player types:
$\tuple{\tau^{reg}, \Delta(A)}$, $\tuple{\tau^{reg}, \bar{\mu}}$ and
$\tuple{\tau^{\pi}, \bar{\mu}}$. The relative proportions of these depend on the initial
population.\todo{check uniform notation for player types: round vs.~square brackets} This
variability disappears if we add a small mutation rate to the dynamics. We assume a fixed,
small mutation rate $\epsilon$ for the probability that a player's preference type \emph{or}
her epistemic type changes to another random preference type or epistemic type. The probability
that a player type randomly mutates into a completely different player type with altogether
different preference type and epistemic type would then be $\epsilon^2$. With these assumptions
about ``component-wise mutations'', numerical simulations of the (discrete time)
\emph{replicator mutator dynamics} \citep{Nowak2006:Evolutionary-Dy} show that already for very
small mutation rates almost all initial populations converge to a single fixed point in which
the majority of players are regret types. For instance, with $\epsilon = 0.001$, almost all
initial populations are attracted to a final distribution with proportions:\todo{recalculate
  these numbers for the actual 4x4 game!}

@@

What this suggests is that, since biological evolution selects behavior-generating mechanisms,
not behavior as such, it need not be the case that behaviorally equivalent mechanisms are
treated equally all the while. If mutation probabilities are a function of individual
components of such behavior-generating mechanisms, it can be the case that certain components
are more strongly favored by a process of random mutation and selection. This is exactly the
case with regret-based subjective preferences in the present example. Since regret-based
subjective preferences are much better in connection with radical uncertainty than veridical
preferences are, the proportion of expected regret minimizers in the attracting state is
substantially higher than that of expected utility maximizers, even though these types are
behaviorally equivalent. In sum, component-wise mutation could have lead to a majority of
regret-based players even if they are behaviorally indiscernible from decision makers with
veridical preferences, because regret types are better off under radical uncertainty.

@@

Results based on the single meta-game in Table~\ref{tab:ExpectedFitness_4Types}, which was
obtained by averaging over numerical simulations, are not fully general and possibly spoiled by
random fluctuations in the sampling procedure. Fortunately, for the case of symmetric
$2 \times 2$ games, the main result that maximin types $(\tau^{\pi}, \Delta(A_{-i}))$ are
strictly dominated can also be shown analytically for generous general conditions on how likely
randomly sampled games are.

@@

  Let $\Lambda = \lbrace (\tau^{\pi}, \Delta(A_{-i})), (\tau^{reg}, \Delta(A_{-i})) \rbrace$ be
  the set of possible meta-types $(\tau, e)$ in the population, and let $\mathcal{G}$ be the class
  of symmetric $2 \times 2$ games with payoffs sampled from a finite, or compact and convex,
  set of i.i.d.~values. Then, $(\tau^{reg}, \Delta(A_{-i}))$ is the only strict Nash
  equilibrium in the resulting meta-game.

@@

Corollary~\ref{corollary1} tells us that the conclusions drawn in the previous section based on
the meta-game in Table~\ref{tab:ExpectedFitness_4Types} hold more generally for any class of
games in which the probability of encountering a game is the product of independently sampling
four identically distributed payoff values. As before, player types
$(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and
$(\tau^{reg}, \overline{\mu})$ will be neutrally stable, and fitness-based selection will tend
to weed out maximin play and leave us with a population of arbitrary frequency of
$(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and
$(\tau^{reg}, \overline{\mu})$ meta-types.

This shows that there is support for the main conceptual point that we wanted to make:
non-veridical subjective preference relations \emph{can}, under specific circumstances, persist
under evolutionary selection based on objective fitness. Moreover, regret-based preferences can
not only persist, but even be favored by natural selection if agents are radically
uncertain. This holds generally for playing arbitrary $2 \times 2$ games whose payoffs are
sampled identically and independently at random.

@@

How do the basic results from the previous section carry over to more encompassing, richer
models? Section~\ref{sec:more-types} first considers further conceptually interesting
preference types that have been suggested in the recent literature. Section~\ref{sec:n-times-n}
then considers the case of $n \times n$ games for $n \ge 2$. Finally, to put our results into
the proper perspective, Section~\ref{sec:solitary-decisions} ends with a brief comparison of
game situations with cases of solitary decision making.

@@

The approximations in Table~\ref{tab:ExpectedFitness_2x2_Full} confirm basic intuitions about
altruistic and competitive types: averaging over randomly sampled games, everybody would like
to have an altruistic opponent and nobody would like to play against a competitive
opponent. Perhaps more surprisingly, altruistic types come up strictly dominated by competitive
types, but competitive types themselves are worse off against all opponent types except against
maximin players $\tuple{\tau^{\pi}, \Delta(A)}$ than any of the behaviorally equivalent types
$(\tau^{reg}, \Delta(A_{-i}))$, $(\tau^{\pi}, \overline{\mu})$, and
$(\tau^{reg}, \overline{\mu})$.  This is a noteworthy results in the light of the fact that
evolving altruistic preferences have been shown to support cooperative behavior in a single
stage game \myalert{[CITE]}. \todo{@Paolo: check whether this is true, please!} In contrast,
averaging over payoffs in multiple stage games, like we do here, makes altruistic preferences
prime victims of evolutionary eradication.

It is easy to see then that the previous result still obtains for the larger meta-game in
Table~\ref{tab:ExpectedFitness_2x2_Full}: $(\tau^{reg}, \Delta(A_{-i}))$,
$(\tau^{\pi}, \overline{\mu})$, and $(\tau^{reg}, \overline{\mu})$ are still neutrally stable;
all simulations of the (discrete-time) replicator dynamic on the $8 \times 8$ meta-game from
Table~\ref{tab:ExpectedFitness_2x2_Full} end up in populations consisting of only these types
in arbitrary proportion.

The following proposition (partially) confirms this result.\todo{rephrase to acknowledge all
  epistemic types?}

@@

Results from Section~\ref{sec:results:-basic-model} relied heavily on
Fact~\ref{fact:equivalence2x2} that, for the special case of $2 \times 2$ symmetric games,
regret minimization $\tuple{\tau^{reg}, \Delta(A)}$ is behaviorally equivalent with expected
regret minimization $\tuple{\tau^{reg}, \bar{\mu}}$ and expected utility maximization
$\tuple{\tau^{\pi}, \bar{\mu}}$. This is no longer true when we look at arbitrary $n \times n$
games with $n \ge 2$. Table~\ref{tab:ExpectedFitness_10x10} therefore gives approximations for
expected fitness in a meta-game over a class of $n \times n$ symmetric games where
$n$ is randomly drawn from $\set{2, \dots, 10}$. Concretely, the numbers in
Table~\ref{tab:ExpectedFitness_10x10} are averages of payoffs obtained in 100,000 randomly
sampled games, where each game was sampled by first picking a number of acts
$n \in \set{2, \dots, 10}$ uniformly at random, and then filling the resulting $n \times n$
payoff matrix of the stage game with i.i.d.~sampled payoffs as before.
